\documentclass[10pt]{article}

\usepackage{ifthen}
\usepackage{geometry}
\usepackage[usenames,dvipsnames]{color}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{url}
\usepackage{multicol}
\usepackage{paracol}
\usepackage{fontspec}
\usepackage{xeCJK}
\usepackage{changepage}
\usepackage{listings}

\thispagestyle{empty}\pagestyle{empty}

\XeTeXlinebreaklocale "zh"
\setCJKmainfont{Source Han Serif SC}

\input{cv.tex}

\begin{document}

\cvtitle{\textbf{Zhang YiFei}}{BrickRed}{Software Engineerer}{0.5cm}

\positionedbox{left}{0.7\textwidth}{%
	Phone: +86 13032883129\\
	Mail: \url{flynn.zhang@foxmail.com}\\
	Blog: \url{https://blog.simplenaive.cn}\\
	Github: \url{https://github.com/Yidadaa}
}
% \positionedbox{right}{0.3\textwidth}{UESTC\\Chengdu, China}

\vspace{0.3cm}

\setlength{\columnsep}{1cm}
\begin{multicols}{2}
		\cvsectiontitle{\textbf{Education}}
		\cvcompany{MSc. UESTC}{2018.09 - 2021.06}\\
		Computer Science, Dept. of Computer Science and Engineering

		\cvcompany{B.Eng. UESTC}{2014.09 - 2018.06}\\
		Computer Science, Yincai Honors College of UESTC

		\columnbreak

		\cvsectiontitle{\textbf{Honors}}
		\vspace{-0.5cm}

		\cvcompany{\small{Second Prize for Postgraduate Scholarship}}{2019.10}\\%
		\cvcompany{\small{OPPO AI Challenge Segmantation Track \\Excellence Prize}}{2019.04}\\%
		\cvcompany{\small{First Prize for Postgraduate Scholarship}}{2018.10}\\%
		\cvcompany{\small{MCM Honorable Mention}}{2017.02}
\end{multicols}
	
		\vspace{0.3cm}
		\cvsectiontitle{\textbf{Experience}}
		\vspace{-1cm}
		\begin{itemize}[leftmargin=0.5cm]
		\item \cvcompany{Research Software Engineer Intern @ Tencent.Inc AI Lab Robotics X}{2019.11 - 2020.06}\cvsublevel{%
			\cvsubbullet{%
				Survey and optimize real-time 3d reconstruction algorithms, implemented Kinect camera driver for %
				Elastic Fusion 3D reconstruction algorithm, implemented the ROS message passing interface for Voxblox %
				and ORB-SLAM.
			}% 
			\cvsubbullet{%
				Developed a real-time point cloud data streaming algorithm, and optimize the latency and robustness of the %
				algorithm.
			}
			\cvsubbullet{
				Developed a virtual reality robot control system, combined 3D real-time reconstruction, dynamic calibration and %
				high-performance 3d rendering.
			}
			\cvsubbullet{%
				\textbf{Keywords:} 3D Reconstruction, SLAM, Real-Time Data Streaming, C++
			}
		}
		% \item \cvcompany{Accelerate reinforcement algorithm training in Unity @ Thesis}{2017.10 - 2018.06}\cvsublevel{%
		% 	\cvsubbullet{Reinforcement learning agent often needs a large number of exploration data to optimize policy %
		% 		by interacting with the environment. It will take a high time and material cost in the real world. We propose %
		% 		a framework that allows existing algorithms to interact with Unity environment and collect data in real-time. %
		% 	}
		% }
		\item \cvcompany{Software Engineer (Part-Time \& Remote) @ Sibbay.Inc}{2017.12 - 2019.03}\cvsublevel{%
			\cvsubbullet{%
				Sibbay.Inc builds a new fitness and health data sharing community for the people, provides a private and secure %
				health data sharing system for users and their doctors.
			}%
			\cvsubbullet{%
				Worked as a remote part-time developer, developed the wechat mini-program with other web developers. %
			}%
			\cvsubbullet{%
				Designed and validated new features in online meetings. Built and optimized the workflow based on Github, %
				reviewed the code and ensured the quality of the source code.%
			}
			\cvsubbullet{%
				Balanced requirements, UX, and deadlines in order to get most of the business value in a limited timeframe.%
			}
			\cvsubbullet{%
				\textbf{Keywords:} Web Development, Team Cooperation, Vue, Git Workflow
			}%
		}
		\item \cvcompany{Software Engineer Intern @ Baidu.Inc}{2016.12 - 2017.05}\cvsublevel{%
			\cvsubbullet{%
				Baidu FengChao is the core marketing department of Baidu.Inc, provides marketing services for %
				over 8 hundred thousand of enterprise users.
			}%
			\cvsubbullet{%
				Implemented the new features of Baidu advertisement system, %
				worked with UI/UX designer, PM, QA and backend developer and bridged the gap between graphical design %
				and technical implementation, optimized application for maximum speed and scalability, and built reusable %
				code for future use.
			}%
			\cvsubbullet{%
				\textbf{Keywords:} Web Development, Team Cooperation, React \& Redux, Git Workflow
			}%
		}
		\end{itemize}

		\vspace{0.4cm}
		\cvsectiontitle{\textbf{Projects \& Skills}}
		\vspace{-0.8cm}

		\begin{adjustwidth}{0.1cm}{0cm}
			\cvcompany{\project{github.com/Yidadaa/Pytorch-Video-Classification}{Python / Pytorch}{$\approx 500$ lines}}{2019.04}\\
				\textit{Make Action Classification on Videos using CNN-RNN, achieves 80\% accuracy on UFF101 Dataset.}

			\vspace{0.1cm}
			\cvcompany{\project{github.com/Yidadaa/Satellite-Imagery-Segmantation-Deeplab}{Python / Pytorch}{$\approx 1000$ lines}}{2019.05}\\
				\textit{Satellite Imagery Segmantation using Deeplabv3.}

			\vspace{0.1cm}
			\cvcompany{\project{github.com/Yidadaa/Parallel-Programming-On-GPU}{CUDA / C++}{$\approx 200$ lines}}{2018.11}\\
				\textit{Accelerate simulation of n-body problem using CUDA, 3000x faster after accelerating.}
			
			\vspace{0.1cm}
			\cvcompany{\project{github.com/Yidadaa/Captcha-Deep-Learning}{Python / Keras / Tensorflow}{$\approx 500$ lines}}{2018.01}\\
				\textit{Recognize captcha using an End-to-End CNN pipeline, achieves 98\% accuracy on custom Dataset.}
			
			\vspace{0.1cm}
			\cvcompany{\project{github.com/Yidadaa/OPPO-Human-Segmentation}{C++ / Dart}{$\approx 1000$ lines}}{2019.03}\\
				\textit{Deploy deeplabv3 human segmantation model to mobile platform using Tencent NCNN framework.}
			
			\vspace{0.1cm}
			\cvcompany{\project{github.com/Yidadaa/HUAWEI-Codecraft-2019}{C++}{$\approx 1000$ lines}}{2019.05}\\
				\textit{Code for HUAWEI Codecraft 2019, contains unit testing, following Google C++ Style Guide.}
		\end{adjustwidth}

\end{document}
